Income Has Serious Implications On Many Facets of American Life in 2021.

### 2022-03-22 outputs/paper/paper.Rmd
FINAL COMMIT

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021"
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On The Veracity of American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: https://github.com/adam-labas/The-US-GSS-And-The-American-Dream"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The American Dream is the idea that, as a nation, the United States embodies freedom that includes financial success, upward social mobility for families and children, as well as freedom to live as they please in a society with few barriers. We obtained and analyzed data from the 2021 United States General Social Survey, focusing on the relationship between the distribution of past and present income and various external demographic categories. We find that the data’s limitations limit our findings, where the analysis points to a heavy skew in income across all demographics however, the uneven bin width, income cutoff and small sample size obstruct us from taking our implications at face value. Although our findings have implications for the theory of the American Dream, due to the limitations we choose to create a stand alone supplementary survey that will aid us for our purposes."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

>>>>

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021."
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On The Veracity of American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: https://github.com/adam-labas/The-US-GSS-And-The-American-Dream"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The American Dream is the idea that, as a nation, the United States embodies freedom that includes financial success, upward social mobility for families and children, as well as freedom to live as they please in a society with few barriers. We obtained and analyzed data from the 2021 United States General Social Survey, focusing on the relationship between the distribution of past and present income and various external demographic categories. We find that the data’s limitations limit our findings, where the analysis points to a heavy skew in income across all demographics however, the uneven bin width, income cutoff and small sample size obstruct us from taking our implications at face value. Although our findings have implications for the theory of the American Dream, due to the limitations we choose to create a stand alone supplementary survey that will aid us for our purposes."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---
